Illuminating a Dark Lens : A Type Ia Supernova Magnified by \\ the Frontier Fields Galaxy Cluster Abell 2744

### 2015-08-11 APJ.submitted/snTomas.tex
Modified source plane minimization discussion

\smallskip
\change{{\it (2) Strong vs. Strong+Weak:}}
\change{Thirteen of the mass models evaluated here are constrained only using
strong-lensing features such as multiply-imaged background galaxies
and highly magnified arcs.  There are now $\sim$150 known lensed
images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
located several arcseconds outside the core region of the cluster
where these multiply-imaged galaxies are found.  Therefore these
``strong-lensing only'' models must necessarily rely on extrapolations
to provide a prediction for the SN \tomas\ magnification.}

@@

\subsubsection{Misidentification of a multiple image}
\citet{Jauzac:2014c} proposed a correction
for the location of image 3.3, the third component of a triply-imaged
galaxy \citep{Merten:2011} at $z=3.98\pm0.02$ \citep{Johnson:2014}.
This possibly specious multiple image is only $\sim$10\arcsec\ from
the SN \tomas\ position, meaning a change in its location could have a
large impact on the predicted magnification for
SN \tomas\ \citep[see][for a quantitative discussion of this
effect]{Johnson:2014}.  However, \citet{Jauzac:2014c} also evaluated a
version of the CATS(v2) model in which this single source is left in
the original position and found that the location of image 3.3 does
not significantly affect the predicted magnifications.  Furthermore,
dividing our 17 models into those using the original location vs those
that adopt the new position, we find that both groups include models
that are within 1$\sigma$ of the observed $\mu$ as well as
significantly discrepant points.

@@

There are several strategies for mitigating this well known bias.
Optimizing a model in the image plane can avoid this bias
entirely \citep{Broadhurst:2005,Zitrin:2009a}. The
Sharon(v2), Zitrin-LTM, Zitrin-NFW, and CATS(v2-2.2) models all use
image plane minimization.  Alternatively, one may guard against this
bias by using a modified source plane minimization that is constrained
not to generate overly small de-lensed
sources \citep{Sendra:2014,Diego:2014}. In our test set, this
second strategy is employed by the Diego model. 
\change{ Similarly, the Williams model uses source plane optimization 
in the GRALE algorithm, but avoids bias by maximizing the {\it
fractional} overlap of extended sources plane images.}  Finally, the
effect of this bias should be reduced when one uses many strong
lensing constraints over a wide range of redshifts. The CATS(v2) and
CATS(v2.1) models have the largest number of strong-lensing
constraints, using 50 and 55 multiply-imaged systems, respectively.

Although many of the tested models utilize these 
strategies to prevent a source plane minimization bias,
Table~\ref{tab:PredictedMagnifications} and
Figure~\ref{fig:LensingTest} show that these models do not uniformly
deliver more accurate magnification predictions.  The most direct test
of this is in the Sharon and CATS model series.  
\change{Both of these model series use the LENSTOOL 
software \citep{Kneib:1996,Jullo:2007,Jullo:2009,Kneib:2011a}, which
allows a choice of how the minimization is done.  For both the Sharon
and CATS model sets,} the v1 model used the faster source plane
minimization approach, but the v2 model was constructed with the more
costly image plane minimization.  Neither of those models show a
significant improvement in model accuracy from v1 to v2.  This
provides a strong indication that the observed tension between models
and the SN observation cannot be entirely attributed to a bias arising
from source plane minimization.

@@

\input{snTomas.bbl}

%\bibliographystyle{apj}
%\bibliography{bibdesk}

>>>>

\smallskip
\change{{\it (2) Strong vs. Strong+Weak:}}
\change{Thirteen of the mass models evaluated here are constrained only using
strong-lensing features such as multiply-imaged background galaxies
and highly magnified arcs.  There are now $\sim$150 known lensed
images behind Abell 2744 \citep{Jauzac:2015b}, but SN \tomas\ is
located several arcseconds outside the core region of the cluster
where these multiply-imaged galaxies are found.  Therefore these
``strong-lensing only'' models must necessarily rely on extrapolations
to provide a prediction for the SN \tomas\ magnification.}

@@

\subsubsection{Misidentification of a multiple image}
\citet{Jauzac:2015b} proposed a correction
for the location of image 3.3, the third component of a triply-imaged
galaxy \citep{Merten:2011} at $z=3.98\pm0.02$ \citep{Johnson:2014}.
This possibly specious multiple image is only $\sim$10\arcsec\ from
the SN \tomas\ position, meaning a change in its location could have a
large impact on the predicted magnification for
SN \tomas\ \citep[see][for a quantitative discussion of this
effect]{Johnson:2014}.  However, \citet{Jauzac:2015b} also evaluated a
version of the CATS(v2) model in which this single source is left in
the original position and found that the location of image 3.3 does
not significantly affect the predicted magnifications.  Furthermore,
dividing our 17 models into those using the original location vs those
that adopt the new position, we find that both groups include models
that are within 1$\sigma$ of the observed $\mu$ as well as
significantly discrepant points.

@@

There are several strategies for mitigating this well known bias.
Optimizing a model in the image plane can avoid this bias
entirely \citep{Broadhurst:2005,Zitrin:2009a}. The Sharon(v2),
Zitrin-LTM, Zitrin-NFW, and CATS(v1,v2-2.2) models all use image plane
minimization.  Alternatively, one may guard against this bias by using
a modified source plane minimization that is constrained not to
generate overly small de-lensed
sources \citep{Sendra:2014,Diego:2014}. In our test set, a version of
this second strategy is employed by the \change{GLAFIC, Williams, and
Diego} models.  \change{For example, the Williams model uses source
plane optimization in the GRALE algorithm, but avoids bias by
maximizing the {\it fractional} overlap of extended source plane
images.}  Finally, the effect of this bias should be reduced when one
uses many strong lensing constraints over a wide range of
redshifts. The CATS(v2) and CATS(v2.1) models have the largest number
of strong-lensing constraints, using 50 and 55 multiply-imaged
systems, respectively.

Although most of the tested models utilize one of these 
strategies to prevent a source plane minimization bias,
Table~\ref{tab:PredictedMagnifications} and
Figure~\ref{fig:LensingTest} show that these models do not uniformly
deliver more accurate magnification predictions.  The most direct test
of this is in the Sharon and CATS model series.  
\change{Both of these model series use the LENSTOOL 
software \citep{Kneib:1996,Jullo:2007,Jullo:2009,Kneib:2011a}, which
allows a choice of how the minimization is done.  For the Sharon
series, the v1 model used the faster source plane minimization
approach, but the v2 model was constructed with the more accurate
image plane minimization.  The CATS v1, 2, 2.1, and 2.2 models all
used image plane optimization, while the v1.1 employed source plane
optimization (and also added in weak lensing constraints).  In neither
of these model series do we see a uniform improvement in accuracy when
optimization is done in the image plane.  This test strongly suggests
that the observed tension between the lens models and the SN
observation cannot be entirely attributed to a bias arising from
source plane minimization.}

@@

%\input{snTomas.bbl}

\bibliographystyle{apj}
\bibliography{bibdesk}
